CGM and OGTT Categories

### 2025-03-13 Christine Chan/EnVision CF/christine_CGM_OGTT_category.qmd
clean data for Katie to check

@@

@@

@@

```{r}
#| label: fig-1
#| fig-cap: Percentages by visit
#| fig-width: 12
#| fig-height: 8
df %>%
  group_by(study_id) %>%
  mutate(`Visit Num.` = row_number()) %>%
  group_by(`Visit Num.`) %>%
  count(Diagnosis) %>%
  mutate(total = sum(n), perc = n / total) %>%
  ggplot(., aes(x = `Visit Num.`, y = perc, fill = Diagnosis)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = paste0(scales::percent(perc), " (n = ", n, ")")),
    position = position_stack(vjust = 0.5)
  ) +
  theme_bw() +
  theme(
    axis.text.y = element_blank(), axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  )
```

>>>>

Participant `r df$study_id[which(df$scully140=="[17.5, Inf)"& df$Diagnosis=="NGT")]` were categorized as NGT by OGTT but had >=17.5% time over 140 on CGM.

@@

Participants `r df$study_id[which(df$scully180=="[3.4, Inf)"& df$Diagnosis=="NGT")]` were categorized as NGT by OGTT but had >=3.4% time over 180 on CGM.

## CGM metrics by OGTT status

```{r}
df %>%
  select(
    Diagnosis, mean_sensor, standard_deviation, cv,
    percent_time_over_140, percent_time_over_180, percent_time_70_140,
    percent_time_70_180
  ) %>%
  tbl_summary(by = Diagnosis, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

@@

## CGM metrics by OGTT status

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    Diagnosis, mean_sensor, standard_deviation, cv,
    percent_time_over_140, percent_time_over_180, percent_time_70_140,
    percent_time_70_180
  ) %>%
  tbl_summary(by = Diagnosis, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

@@

```{r}
#| label: fig-1
#| fig-cap: Percentages by visit
#| fig-width: 12
#| fig-height: 8
df %>%
  filter(!is.na(Diagnosis)) %>%
  group_by(study_id) %>%
  mutate(`Visit Num.` = row_number()) %>%
  group_by(`Visit Num.`) %>%
  count(Diagnosis) %>%
  mutate(total = sum(n), perc = n / total) %>%
  ggplot(., aes(x = `Visit Num.`, y = perc, fill = Diagnosis)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = paste0(scales::percent(perc), " (n = ", n, ")")),
    position = position_stack(vjust = 0.5)
  ) +
  theme_bw() +
  theme(
    axis.text.y = element_blank(), axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  )
```
